\documentclass[]{article}

\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage[english, polish]{babel}

\usepackage{geometry}
\newgeometry{tmargin=2.5cm, bmargin=2.5cm, lmargin=2.5cm, rmargin=2.5cm}

\setlength{\parindent}{1cm}


\begin{document}
\thispagestyle{empty}
\begin{center}
	\huge
	Uniwerystet Śląski w Katowicach
	
	\vspace{5cm}
		
	\Large
	PROJEKT APLIKACJI WEBOWEJ\\	
	Dokumentacja wstępna projektu
		
	\vspace{1cm}
	
	\textbf{Plate - RSS Reader}
	
	\vspace{10cm}
	
	\large
	wykonał:\\
	Kamil Duda
\end{center}

\selectlanguage{english}

\newpage
\tableofcontents


\newpage
\section{Project overview}
\hspace{0.9cm}
The main goal of the project is to create a fully functional RSS feeds reader as a web application.
Outcome application must allow users to register their accounts, log in and subscribe to feeds they want.
\\In addition, there may be options for categorising and adding feeds to favourites available.\\
Temporary name for the application - Plate.

The secondary objective is to become acquainted with the technologies and frameworks which will be used.


\section{Functional requirements}
\subsection{User stories}
\hspace{0.9cm}
To get the better understanding of the customer's needs, all of the functional requirements were gathered as user stories.
Some of the stories are more abstract or specific than the others; therefore, collected requirements shall be analyzed and transformed into tasks.


\subsection{List of the user stories}

\begin{enumerate}
	\item Registration and logging in\\
	As a user, I want to be able to register my account and log in in order to get access to my personalized aNews.
	
	\item E-mail address as currentPassword\\
	As a user, I want to be able to log in using my e-mail address so that I do not have to remember additional information (login).
	
	\item Facebook and Google accounts\\
	As a user, I want to be able to register and log in using my Facebook or Google account so I do not have to create yet another account.
	
	\item Account management\\
	As a user, I want to be able to manage my account e.g. change my newPassword.
	
	\item Password reset\\
	As a user, I want to be able to recover my lost or forgotten newPassword.
	
	\item Feeds presentation\\
	As a user, I want the application to present me with the latest aNews from the feeds I subscribed to.
	
	\item Feeds from URL\\
	As a user, I want to be able to add RSS feeds to my account using their URL address.
	
	\item Feeds categorizing\\
	As a user, I want to be able to add different feeds to "My favourites" list and other categories so it would be convenient to browse through aNews.
	
	\item Removing feeds\\
	As a user, I want to be able to unsubscribe from unwanted feed so that I will not be overwhelmed with undesirable information. 
	
	\item Grid and list layout\\
	As a user, I want to be able to change the way that the aNews are displayed e.g list or tiles.
	
	\item Appealing UI\\
	As a user, I want this application to have an esthetic interface so it would be pleasant to use it.
	
	\item Responsive UI\\
	As a user, I want to be able to use the application on both computer and mobile phone so I will not be restricted to only one device.
\end{enumerate}


\section{Non-functional requirements}
\hspace{0.9cm}
Besides the functional requirements, there are other concerns of which the customer may nor be aware and which must be fulfilled.


\subsection{List of the non-functional requirements}
\begin{enumerate}
	\item Security\\
	As far as the security is concerned, from the technical point of view, a secure and trustworthy way of authentication and managing user accounts must be provided.
	A proper passwords encryption can be the solution.
	
	\item Extensibility\\
	In regards to extensibility, application must be ready for extension and adding new features. It can be achieved through good system architecture, "clean code" and extensible testing.
	
	\item Testability\\
	Code must be written in a mean that provides an easy way for testing it.
	
	\item Usability\\
	In order to satisfy customer's difficult need for the "appealing user interface", we can utilize the concept of Single Page Application.
	
	
\end{enumerate}

\section{Technology used}
\hspace{0.9cm}
Some of the technologies may not be appropriate for the given project, they were chosen in order to get comfortable using them.

\subsection{List of the used technologies}
\begin{enumerate}
	\item AngularJS\\
	JavaScript Single Page Application framework that makes the creating of SPA app straightforward. Moreover, it comprises a lightweight implementation of JQuery.
	
	\item Bootstrap\\
	HTML, CSS and JS framework for creating responsive and friendly-looking user interfaces.
	
	\item Java Spring Framework\\
	Spring Framework is a powerful and easy-to-use tool for creating application. Along with dependency injection it provides a variety of extensions like: Spring Boot, Spring Web, Spring MVC, Spring Security, Spring Data for MongoDB.
	
	\item Apache Tomcat\\
	This project contemplates the use of either Tomcat's Java servlet module - Catalyna - or even embedded Spring Boot's Tomcat server. This particular server technology was chosen for it is Open Source and has an immense user base that can provide with a helpful support.
	
	\item MongoDB\\
	MongoDB is a modern NoSQL database system. It is highly scalable and provides a top-notch performance. It will be used to store users' accounts information and their RSS feeds.
	
	
\end{enumerate}

\end{document}